Supplementary Information

### 2020-05-26 doc/manuscript/MEE_manuscript.Rmd
update manuscript

### Length planning:
## Main text ~4300 words --> ~28 paragraphs averaging 150 words
# Intro- 900/ 6
# Methods- 1500 / (11)
# Results - 1000/ (6)
# Discussion - 900 / (5)
## References: figure ~40 words each, so 50 refs = 2000
## Display items: figure ~100 words for each caption = 700 words
# Table1- table of sites
# Fig0?- schematic illustrating our process
# Fig1- relationship of ∆r and ∆AGB to DBH (all site-species combinations)
# Fig2- climate senstivity (SCBI example): (a) Helcoski quilt plot, (b) Climwin panel a, (c) GLS output
# Fig3- multipanel- GLS results for climate sensitivity at all sites (3 columns with the 3 variable type groupings, 1 row per site)
# Fig4/ table2- DBH/climate interactions
# Fig 4/5- responses to CO2 and atmospheric deposition

@@

@@

>>>>

### Length planning:
## Main text ~4300 words --> ~28 paragraphs averaging 150 words
# Intro- 900/ 6
# Methods- 1500 / (11)
# Results - 1000/ (6)
# Discussion - 900 / (5)
## References: figure ~40 words each, so 50 refs = 2000
## Display items: figure ~100 words for each caption = 700 words
# Table1- table of sites
# Fig1- schematic illustrating our process
# Fig2- relationship of ∆r and ∆AGB to DBH (all site-species combinations)
# Fig3- climate senstivity (SCBI example): (a) Helcoski quilt plot, (b) Climwin panel a, (c) GLS output
# Fig4- multipanel- GLS results for climate sensitivity at all sites (3 columns with the 3 variable type groupings, 1 row per site)
# Fig5/ table2- DBH/climate interactions
# Fig 6/7- responses to CO2 and atmospheric deposition

@@

**Figure/ Table on climate - DBH interactions?**

@@

**Figure showing effects of CO2, SO2, NOx**
